Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
Small

Our first presentation of these properties assumes a single simple stack
with no sharing between callers and callees: all parameters and return
values are passed in registers.  Later, we show how to refine it to allow
passing of scalar stack data, granting a callee access to the caller's
data. We do not model more sophisticated sharing, such as taking the address
of a variable and treating it like a pointer.
%
Finally, we define integrity and confidentiality properties for a coroutine
system featuring a static layout, in which each coroutine's stack is
constrained to a fixed region of memory.  Though simplistic, this extension
is a step toward concurrency and demonstrates that our approach is flexible
enough to handle more sophisticated styles of control flow.

@@

\begin{itemize}
\item
  We adapt formulations of integrity and confidentiality from language-based security
  to formalize a parameterized {\em stepwise stack-safety} property and argue that it
  captures the intuitive concepts of stack safety~(\cref{sec:lse}). Our model extends to
  argument passing on the stack and to a simple coroutine system.
\item
  We use a property-based randomized testing framework to support the claim
  that this stepwise property is actually enforced by the Depth Isolation policy
  of~\citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:testing}).
\item
  We formalize a weaker but more extensional \emph{observational} variant of the
  stack safety property and argue that it accurately characterizes
  the Lazy Tagging and Clearing policy of~\citet{DBLP:conf/sp/RoesslerD18}
  enhanced with unique tags on each activation~(\cref{sec:lazy}).
\end{itemize}

@@

We are finally ready for our definition of stack safety. We begin
by describing how we model knowledge about the program structure,
then dive into the formal definitions of local state encapsulation and
well-bracketed control flow, which together constitute stack safety\bcp{not
  any more?}.
Initially we will focus on a simple stack model, with a single stack
that doesn't share between caller and callee. All arguments are passed
in registers. Recall that we keep track of which addresses are
annotated as calls, with a ``code map'':
\[\codemap \in \CODEMAPS \subseteq \WORDS\]
\apt{Doesn't match previous definition any more.}

We parameterize over the structure of the stack, particularly the means by
which a caller identifies the data that should be protected during a call. We term
this the {\em sealing convention}, \(\sealcon \subseteq \MACHS \times \COMPONENTS\), which
maps a machine state to a set of addresses. \apt{Is it a relation or a function (seems to
  be the latter)?}
If a state's \(\PCname\) is annotated as a call, the sealing convention tells us
which addresses must be protected until the return. Similarly, we abstract over what
it means to return with a {\em return convention}, \(\retcon \subseteq \MACHS \times \MACHS\),
which relates call states to the states that can be considered valid returns to that call.
The usual return convention is that \(\mach\) and \(\mach'\) agree on the stack pointer,
and \(\mach'\) has its program counter advanced by one instruction from \(\mach\).
But whatever the return convention, at each step we update the context according
to the context-step function, \(\stepsto_C\).\apt{abrupt transition}

@@

The rules for \(\stepsto_C\) are given inductively, and apply in the listed order.
A call annotation tells us to push the return target onto the return stack and
seal all components with the depth of the previous return stack. If we aren't making a call,
we identify a return by looking ahead and checking if we're about to step to a state
that matches the topmost return target. If neither is true, the context remains unchanged.

@@

\subsection{Stack Safety with Passing}

@@

\subsection{Coroutine Safety}

>>>>

Our first presentation of these properties assumes a single simple stack
with no sharing between callers and callees: all parameters and return
values are passed in registers.  Later, we show how to refine it to allow
passing of scalar stack data, granting a callee access to the caller's
data. (We do not consider more sophisticated forms of sharing, such as
taking the address of a variable and treating it like a pointer.)
%
Finally, we define integrity and confidentiality properties for a coroutine
system with a static layout, in which each coroutine's stack is constrained
to a fixed region of memory.  Though simplistic, this extension is a step
toward full-blown concurrency and demonstrates that our approach is flexible
enough to handle more sophisticated styles of control flow.

@@

\begin{itemize}
\item
  We adapt formulations of integrity and confidentiality from language-based security
  to formalize a parameterized {\em stepwise stack-safety} property and argue that it
  captures the intuitive concepts of stack safety~(\cref{sec:lse}). Our model extends to
  argument passing on the stack and to a simple coroutine system.
\item
  We use a property-based randomized testing framework to validate the claim
  that this stepwise property is actually enforced by the {\em Depth Isolation} policy
  of~\citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:testing}).
\item
  We formalize a weaker but more extensional \emph{observational} variant of the
  stack safety property and argue that it accurately characterizes a small
  refinement of
  the {\em Lazy Tagging and Clearing} policy
  of~\citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:lazy}).
\end{itemize}

@@

We are finally ready for our definition of stack safety. We begin
by describing how we model knowledge about the program structure,
then dive into the formal definitions of local state encapsulation and
well-bracketed control flow, which together constitute stack safety\BCP{need
  to put back WBCF!}.

\subsection{Parameters in Registers}

To begin, we will focus on a simple stack model, with a single stack
that doesn't share between caller and callee: arguments and results are passed
in registers.

To accommodate different machine architectures and different calling
conventions, we parameterize over the structure of the stack, particularly
the means by 
which a caller identifies the data that should be protected during a call. We term
this the {\em sealing convention}, \(\sealcon \subseteq \MACHS \times \COMPONENTS\), which
maps a machine state to a set of addresses. \apt{Is it a relation or a function (seems to
  be the latter)?}
If a state's \(\PCname\) is annotated as a call, the sealing convention tells us
which addresses must be protected until the return. Similarly, we abstract over what
it means to return with a {\em return convention}, \(\retcon \subseteq \MACHS \times \MACHS\),
which relates call states to the states that can be considered valid returns to that call.
The usual return convention is that \(\mach\) and \(\mach'\) agree on the stack pointer,
and \(\mach'\) has its program counter advanced by one instruction from \(\mach\).
But whatever the return convention, at each step we update the context according
to the context-step function, \(\stepsto_C\).\apt{abrupt transition}

@@

The rules for \(\stepsto_C\) are given inductively, and apply in the listed order.
A call annotation tells us to push the return target onto the return stack and
seal all components with the depth of the previous return stack. If we aren't making a call,
we identify a return by looking ahead and checking if we're about to step to a state
that matches the topmost return target. If neither is true, the context remains unchanged.
%
\bcp{(Moved this here, BTW.)}Recall that we keep track of which addresses are
annotated as calls, with a ``code map'' $\codemap \in \CODEMAPS \subseteq
\WORDS$.
\apt{Doesn't match previous definition any more.}

@@

\subsection{Parameters Passed on the Stack}

@@

\subsection{Coroutines}
